---
title: "Homework #4"
author: "Student: Thanh Hung Duong"
date: "October 25, 2019"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

### Question 1

```{r 1, results='hold',echo=FALSE}
#Set location
loca="C:/Users/Duong Hung/OneDrive - University Of Houston/MSDS/Fall/6357/HW"
setwd(loca)
fil_nam="HW4.3.txt"
df =  file(fil_nam, open = "r") #open file
dat=NULL
k=1 #index of dat set
f1=c('B1','B2','B3','B4','B5')
f2=c('C1','C2','C3','C4')
rows=1
#Read each line of the data file
while (length(oneLine <- readLines(df, n = 1, warn = FALSE)) > 0) {
  num_lis = (strsplit(oneLine, " ")) #List of values in 1 line
  num_lis = as.numeric(num_lis[[1]]) # Convert them to numeric
  #Category the imported data
  interval=length(num_lis)
  for (i in 1:interval){
    dat$bolt[k]=f1[i]
    dat$chem[k]=f2[rows]
    dat$ts[k]=num_lis[i]
    k=k+1
  }
  rows=rows+1
} 
close(df)
dat=data.frame(dat)
##############

fit=aov(ts~chem+bolt,data=dat)
summary(fit)
summary.lm(fit)
TukeyHSD(fit, which = "chem")
print('Chemical    Mean   SD')
for (i in 1:4){
  rows=dat$ts[dat$chem==f2[i]]
  print(paste('  ',f2[i],'     ',mean(rows),' ',round(sd(rows),2)))
}

```

Comment:

\hrulefill

\hrulefill

\hrulefill

\hrulefill

\hrulefill

## Question 2: potential differences between nozzle designs,with velocity

```{r 2,echo=FALSE}
fil_nam="HW4.10.txt"
df =  file(fil_nam, open = "r") #open file
dat=NULL
k=1 #index of dat set
velo=c('11.73', '14.37', '16.59', '20.43', '23.46', '28.74')
desi=c('D1','D2','D3','D4','D5')
rows=1
#Read each line of the data file
while (length(oneLine <- readLines(df, n = 1, warn = FALSE)) > 0) {
  num_lis = (strsplit(oneLine, " ")) #List of values in 1 line
  num_lis = as.numeric(num_lis[[1]]) # Convert them to numeric
  #Category the imported data
  interval=length(num_lis)
  for (i in 1:interval){
    dat$jev[k]=velo[i]
    dat$design[k]=desi[rows]
    dat$sf[k]=num_lis[i]
    k=k+1
  }
  rows=rows+1
} 
close(df)
dat=data.frame(dat)
##############   a   ###########
fit=aov(sf~design+jev,data=dat)
summary(fit)
summary.lm(fit)
TukeyHSD(fit, which = "design")
print('Design    Mean   SD')
for (i in 1:5){
  rows=dat$sf[dat$design==desi[i]]
  print(paste('  ',desi[i],'     ',round(mean(rows),4),' ',round(sd(rows),4)))
}
plot(dat$sf~dat$design,xlab='Design',ylab = 'Shape factor',title='Nozzle design vs Shape factor')
print('Analyze the residuals')
par(mfrow=c(2,2))
plot(fit)
print('c). Take velocity as the variable of secondary interest')
fit2=aov(sf~design,data=dat)
summary(fit2)
summary.lm(fit2)
```
Comment:

\hrulefill

\hrulefill

\hrulefill

\hrulefill

\hrulefill

\hrulefill

\hrulefill

## Question 3: Six algorithms were applied to several different software development 
projects and the percent error in estimating the development cost was observed


```{r 3,echo=FALSE}
library(MASS)
fil_nam="HW4.11.txt"
df =  file(fil_nam, open = "r") #open file
dat=NULL
k=1 #index of dat set
coln=c('P1','P2','P3','P4','P5','P6')
rown=c('A1','A2','A3','A4','A5','A6')
rows=1
#Read each line of the data file
while (length(oneLine <- readLines(df, n = 1, warn = FALSE)) > 0) {
  num_lis = (strsplit(oneLine, " ")) #List of values in 1 line
  num_lis = as.numeric(num_lis[[1]]) # Convert them to numeric
  #Category the imported data
  interval=length(num_lis)
  for (i in 1:interval){
    dat$proj[k]=coln[i]
    dat$algo[k]=rown[rows]
    dat$cost[k]=num_lis[i]
    k=k+1
  }
  rows=rows+1
} 
close(df)
dat=data.frame(dat)
##############   a   ###########
fit=aov(cost~algo+proj,data=dat)
summary(fit)
summary.lm(fit)
TukeyHSD(fit, which = "algo")
print('Algorithm    Mean   SD')
for (i in 1:6){
  rows=dat$cost[dat$algo==rown[i]]
  print(paste('  ',rown[i],'     ',round(mean(rows),4),' ',round(sd(rows),4)))
}
plot(dat$cost~dat$algo,xlab='Algorithm',ylab = 'Development Cost',title='Algorithm types vs Software Development Cost')
print('Analyze the residuals')
par(mfrow=c(2,2))
plot(fit)
boxcox(fit)
fit.log=aov(log(cost)~algo+proj,data=dat)
summary(fit.log)
summary.lm(fit.log)
par(mfrow=c(2,2))
plot(fit.log)

```
## Question 4

```{r 3,echo=FALSE}
fil_nam="HW4.4.txt"
df =  file(fil_nam, open = "r") #open file
dat=NULL
k=1 #index of dat set
coln=c('X','Y','Z')
rown=c('Asp','Con','Gra')
rows=1
#Read each line of the data file
while (length(oneLine <- readLines(df, n = 1, warn = FALSE)) > 0) {
  num_lis = (strsplit(oneLine, ", ")) #List of values in 1 line
  num_lis = as.numeric(num_lis[[1]]) # Convert them to numeric
  #Category the imported data
  interval=length(num_lis)
  i=1
  while (i<=interval){
    dat$brand[k]=coln[(i-1)%/%4+1]
    dat$road[k]=rown[rows]
    dat$tl[k]=num_lis[i]
    i=i+1
    k=k+1
  }
  rows=rows+1
} 
close(df)
dat=data.frame(dat)
####################
options(contrasts = c("contr.treatment", "contr.poly")) 
fit1=aov(tl~road+brand+road*brand,data=dat)
summary.lm(fit1)
#relevel the data to 2
l=2
dat = within(dat, brand <- relevel(brand, ref = l),road <- relevel(road, ref = l))
fit1=aov(tl~road+brand+road*brand,data=dat)
summary.lm(fit1)
#relever the data to 3
l=3
dat = within(dat, brand <- relevel(brand, ref = l),road <- relevel(road, ref = l))
fit1=aov(tl~road+brand+road*brand,data=dat)
summary.lm(fit1)
#Centralization side condition for data
options(contrasts = c("contr.sum", "contr.poly")) 
fit2=lm(tl~road+brand+road*brand,data=dat)
summary(fit2)
dummy.coef(fit2)
fit=aov(tl~road+brand,data=dat)
#Compare the effects of factors
fit.tukey=TukeyHSD(fit)
print(fit.tukey)
plot(fit.tukey)
```


\pagebreak

```{r ref.label='1',eval=FALSE,}
```
```{r ref.label='2',eval=FALSE,}
```
```{r ref.label='3',eval=FALSE,}
```
