---
title: "6.18 and 6.23"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Commercial properties

A commercial real estate company evaluates vacancy rates, square
footage, rental rates, and operating expenses for commercial properties in a large metropolitan
area in order to provide clients with quantitative information upon which to make rental decisions. The data below are taken from 81 suburban commercial properties that are the newest,
best located, most attractive, and expensive for five specific geographic areas.

```{r cars}
# Import input
loca="C:/Users/Duong Hung/OneDrive - University Of Houston/Msds classes materials/Fall semester/Math 6357-01 Linear models"
setwd(loca)
data=read.table("CH06PR18.txt")
#Rename data
names(data)=c('Y','X1','X2','X3','X4')

# Plot the scatter plot of all variables. Comment on the plots.
for (i in 1:4){
  par(mfrow=c(1,1))
  plot(data[,i+1],data$Y,xlab = paste('X',i,sep = ""), ylab = 'Y',col='black',pch=14+i)
}
```

## Fit a regression line to the data
Using the hypothesis testing method to determine the
final model at the significance level of α =0.05. Provide the parameter estimates, standard
errors and 95% confidence intervals of the parameters.

```{r fit}
#Build matrix X
one_vec=data.frame(c(rep(1,81)))
names(one_vec)='1'
X=data.matrix(cbind(one_vec,data[,2:5]))
#Build matrix Y
Y=data.matrix(data$Y)
#Calculate beta_hat
beta=solve(t(X)%*%X)%*%t(X)%*%Y
print('vector beta hat is')
print(beta)
#Calculate fitted values
Y_hat=X%*%beta
#Calculate residuals
res=Y-Y_hat
#print(res)
#Calculate matrix H
h_mtx=X%*%solve(t(X)%*%X)%*%t(X)
i_mtx=diag(81)
#residual sum of squares
sse=t(Y)%*%(i_mtx-h_mtx)%*%Y

mse=sse/(81-5)
s=mse^0.5
c_mtx=solve(t(X)%*%X)
#Distribution of beta hat
var_b=mse[1,1]*c_mtx
#standard error for each beta
ses=NULL
for (i in 1:5){
  ses[i]=sqrt(var_b[i,i])
}
print('standard error for each beta')
print(ses)
sig_lev=0.05
t_val=qt(1-sig_lev/2,81-5)
ci=array(0,c(5,2))
for (i in 1:5){
  ci[i,1]=beta[i]-t_val*ses[i]
  ci[i,2]=beta[i]+t_val*ses[i]
}
print('Confident interval for each beta')
print(ci)
```
## c) Conduct the model diagnostic check, and conclude with the best model for the given data.

```{r}
fit=lm(Y~X1+X2+X3+X4,data = data)
plot(fit)
```
## Textbook Ch 6, Problem 6.21. Calculate the confidence intervals and prediction intervals of 95% for the 3 properties with the given feature.
```{r}
x_0=c(1,1,1)
x_1=c(4,6,12)
x_2=c(10,11.5,12.5)
x_3=c(0.1,0,0.32)
x_4=c(80000,120000,340000)
ndata=data.frame(X1=x_1,X2=x_2,X3=x_3,X4=x_4)
predict(fit,ndata,interval = 'confidence',level = 0.95)
predict(fit,ndata,interval = 'prediction',level = 0.95)
```